### 2023-02-10 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_interpreting_probabilities@126a65373848fd673cccf86b0766cd1d8bf98a39 🚀

As opposed to metawebs, probabilistic local food webs represent the
likelihood that two species will interact at a specific location and
within a given time period; in other words, they are context dependant.
To be specific, space is defined here as the geographic coordinates \$
\mathbf x, \mathbf y\$ of the spatial boundaries delineating the system,
whereas time is the time interval \$ \mathbf t\$ during which
interactions were sampled or for which they were predicted. We put these
variables in bold to emphasize that they are not single values, but
rather continued dimensions that could be outlined differently depending
on the study system. Regardless of how they were defined, they always
delineate a specific area \(A\) and duration \(D\). These could refer to
the sampled area and duration or to the targeted location and time
period.

Many factors could be taken into consideration when estimating the
probability that a predator species \(i\) interacts with a given prey
species \(j\) locally. One of the most important is species
co-occurrence, which describes if both species can be found at location
and time \$ \mathbf x, \mathbf y, \mathbf t\$. Surely, the probability
that the interaction is realized must be \(0\) when species do not
co-occur. Similarly, species relative abundance is another important
predictor of the probability of interaction, because it impacts the
probability that species will randomly encounter (Canard \emph{et al.}
2012; Canard \emph{et al.} 2014; Poisot \emph{et al.} 2015). Interaction
probabilities can also be conditional on other biological and
environmental variables, such as temperature, precipitation, presence of
shelters, phenotypic plasticity, phenology, and presence of other
interacting species in the network. These conditions can affect species
traits, which greatly impact the likelihood of interactions (Poisot
\emph{et al.} 2015). When probabilities of interactions are estimated
using specific values of these variables, ecologists should make them
explicit in their metadata, preferably using mathematical equations to
avoid any ambiguity. In the next section, we will see examples of why
this matters when it comes to spatial, temporal, and taxonomic scaling
of biotic interactions. Here, we will use the variable \(\bold \Omega\)
as a substitute for the biological and ecological context in which
interaction probabilities were estimated. This gives us the following
equation for the probability that species (or taxa) \(i\) and \(j\)
interact in a local network \(N\):

>>>>

As opposed to metawebs, probabilistic local food webs represent the
likelihood that two species will interact at a specific location and
within a given time period; in other words, they are context dependant.
To be specific, space is defined here as the geographic coordinates \$
\mathbf{x}, \mathbf{y}\$ of the spatial boundaries delineating the
system, whereas time is the time interval \$ \mathbf{t}\$ during which
interactions were sampled or for which they were predicted. We put these
variables in bold to emphasize that they are not single values, but
rather continued dimensions that could be outlined differently depending
on the study system. Regardless of how they were defined, they always
delineate a specific area \(A\) and duration \(D\). These could refer to
the sampled area and duration or to the targeted location and time
period.

Many factors could be taken into consideration when estimating the
probability that a predator species \(i\) interacts with a given prey
species \(j\) locally. One of the most important is species
co-occurrence, which describes if both species can be found at location
and time \$ \mathbf{x}, \mathbf{y}, \mathbf{t}\$. Surely, the
probability that the interaction is realized must be \(0\) when species
do not co-occur. Similarly, species relative abundance is another
important predictor of the probability of interaction, because it
impacts the probability that species will randomly encounter (Canard
\emph{et al.} 2012; Canard \emph{et al.} 2014; Poisot \emph{et al.}
2015). Interaction probabilities can also be conditional on other
biological and environmental variables, such as temperature,
precipitation, presence of shelters, phenotypic plasticity, phenology,
and presence of other interacting species in the network. These
conditions can affect species traits, which greatly impact the
likelihood of interactions (Poisot \emph{et al.} 2015). When
probabilities of interactions are estimated using specific values of
these variables, ecologists should make them explicit in their metadata,
preferably using mathematical equations to avoid any ambiguity. In the
next section, we will see examples of why this matters when it comes to
spatial, temporal, and taxonomic scaling of biotic interactions. Here,
we will use the variable \(\bold \Omega\) as a substitute for the
biological and ecological context in which interaction probabilities
were estimated. This gives us the following equation for the probability
that species (or taxa) \(i\) and \(j\) interact in a local network
\(N\):
